Plots for Latent Hawkes Paper

### 2021-05-14 output_scripts/Paper_Plots.Rmd
reduce the base rates for simulations

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
# width=600,height=300)

@@

p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 100) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method")
```

@@

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
# width=600,height=300)
p3_slides <- temp_plot_df %>%
  filter(method != "I-MMHP") %>%
  rowwise() %>%
  #mutate(norm = min(norm,100)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 80) +
  NULL
p3_slides
```

@@

```{r fig-10b-rank-correlation}
par(mar=c(3,5,3,1))
cx <- 1.75  # cex for axis label text; 
# default is 1. bigger numbers make the text bigger, smaller, smaller.  
x.ttl <- ""; # blank x-axis label  
y.ttl <- "rank corr. (expert rank)";  
ttl <- "(b)";  
#y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
# y-axis limits. +2 at top to give room for legend  
y.lim <- c(-1,1.2)    
x.lim <- c(0.5, (length(task.types))) 
cols <- c('paleturquoise4', 'lightgreen', 'cornsilk')
shifts <- c(-0.25, 0, 0.25)

>>>>

temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
# width=600,height=300)

@@

p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot( aes(x = method, y = mae, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("MAE") +
  ylim(0, 8) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method")
```

@@

temp_plot_df <- predict_day_mae_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),
# width=600,height=300)
p3_slides <- temp_plot_df %>%
  filter(method != "I-MMHP") %>%
  rowwise() %>%
  #mutate(norm = min(norm,100)) %>%
  ggplot( aes(x = method, y = mae, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = plot_cols_pred) +
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 10) +
  NULL
p3_slides
```

@@

```{r fig-10b-rank-correlation}
par(mar=c(3,5,3,1))
cx <- 1.75  # cex for axis label text; 
# default is 1. bigger numbers make the text bigger, smaller, smaller.  
x.ttl <- ""; # blank x-axis label  
y.ttl <- "rank corr. (Glicko rank)";  
ttl <- "(b)";  
#y.lim <- c(min(data.tbl$data.value), max(data.tbl$data.value)+.5);
# y-axis limits. +2 at top to give room for legend  
y.lim <- c(-1,1.2)    
x.lim <- c(0.5, (length(task.types))) 
cols <- c('paleturquoise4', 'lightgreen', 'cornsilk')
shifts <- c(-0.25, 0, 0.25)
